\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors

### 2022-07-08 Manuscript/Lanuza_et_al_2022.Rmd
edits

Overall, plant reproductive trait covariation axes help explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales. For example, we found that all floral visitor guilds interacted more frequently with plant species with larger flowers in agreement with previous findings [@hegland2005; @lazaro2013; @kaiser2014]. As predicted by evolutionary life-history theory [@stebbins1970], larger investments on floral display and rewards to attract pollinators makes sense when pollinator dependence is higher but there are compromises (as the flower number - floral display) that can affect the reproductive investment to other organs such as ovule number and affect pollen transfer and seed production

However, the investment in floral display has evident compromises between flower number and flower size

there are evident compromises as the one showed between flower number and flower size that affect the reproductive investment in ovules and pollen transfer as also shown for other wind pollinated species [@friedman2011]

  By combining macroecological patterns with ecological observations, we can show in addition that all floral visitor guilds interacted more frequently with plant species with larger floral displays, in agreement with community level local findings [@hegland2005; @lazaro2013; @kaiser2014]. Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes [@faegri2013; @rosas2014; @dellinger2020]. For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies [name which ones]() and because these two guilds are likely to differ in ecology and behaviour [@rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies. In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive correlations do not.

>>>>

Overall, plant reproductive trait covariation axes help explain observed interaction patterns among and within floral visitor guilds suggesting that plant reproductive strategies partly mediate these associations at large ecological scales. For example, we found that all floral visitor guilds interacted more frequently with plant species with larger flowers and higher pollinator dependence in agreement with previous findings [@hegland2005; @lazaro2013; @kaiser2014]. As predicted by evolutionary life-history theory [@stebbins1970], larger investments on floral display and rewards to attract pollinators makes sense when pollinator dependence is higher but this investment is compromised by the cost of the different reproductive structures, trait associations and the distinct selective pressures such as the one exerted by the different floral visitor guilds [@galen1999]. For instance, smaller flowers were less visited overall, but they are inexpensive (e.g., low ovule number) and can counterpart this lack of visitation at the flower level by increasing the chances of visitation at the whole individual level with larger displays as suggested for wind pollinated species which can optimise the probabilities of pollen capture and seed production with numerous small flowers [@friedman2011]. Because plants can adapt to the most efficient floral visitors [@fenster2004], the different associations found between specific set of traits and floral visitor guilds may indicate the existence of large scale pollination syndromes [@faegri2013; @rosas2014; @dellinger2020]. For instance, bees and syrphid flies were clearly associated with opposing plant reproductive strategies [name which ones]() and because these two guilds are likely to differ in ecology and behaviour [@rader2020; @foldesi2021] they may exert different selective pressures that lead to divergent plant reproductive strategies. In any case, it is worth noting that other local factors such as species relative abundances, surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016] that reproductive correlations do not.
